Clustering in a hyperbolic model of complex networks.

### 2020-05-04 proofs_infinite_k.tex
Corrections to Lemma D 4.1 by Markus
corrected proof Theorem 1.3 and Lemma 6.1

\begin{lemma}\label{lem:clustering_ast_H}
As $n \to \infty$,
\[
	\Exp{\left|c(k_n;G_n) - c^\ast(k_n;G_n)\right|} = \smallO{s(k_n)}.
\]
\end{lemma}

@@

\begin{proofof}{Theorem~\ref{thm:mainktoinfty}}
Note that the second of the theorem follows immediately from the first.

To prove the first statement, we rewrite $c(k_n; G_n)$ as
\begin{align*}
    c(k_n;G_n)-\gamma(k_n) &= \left(c(k_n;G_n)-c^\ast(k_n;G_n)\right)
    	+ \left(c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)\right)\\
    &\hspace{10pt}+ \left(c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right)
    	+ \left(c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)\right)\\
    &\hspace{10pt}+ \E c^\ast(k_n; \Gbox)-\gamma(k_n)
\end{align*}
Then, we take absolute values and apply the triangle inequality. By monotonicity of expectation, we can apply it to both sides and obtain
\begin{align*}
    \Exp{\left|c(k_n;G_n)-\gamma(k_n)\right|} 
    &\le \Exp{\left|c(k_n;G_n)-c^\ast(k_n;G_n)\right|}
    	+\Exp{\left|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)\right|}\\
    &\hspace{10pt}+ \Exp{\left|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right|} 
    	+ \Exp{\left|c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)\right|}\\
    &+ \left|\Exp{c^\ast(k_n; \Gbox)}-\gamma(k_n)\right|
\end{align*}
At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling between the Poissonized KPKVB and the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model.

All of this together yields that:
\begin{align*}
    \Exp{\left|c(k_n;G_n)-\gamma(k_n)\right|} = \smallO{s(k_n)} = \smallO{\gamma(k_n)},
\end{align*}
which establishes the first statement of the theorem and finishes the proof.  
\end{proofof}

>>>>

\begin{lemma}\label{lem:clustering_ast_H}
As $n \to \infty$,
\[
\left|c^\ast(k_n; G_n) - c(k_n; G_n)\right| = \smallOp{s(k_n)}.
\]
%\[
%	\Exp{\left|c(k_n;G_n) - c^\ast(k_n;G_n)\right|} = \smallO{s(k_n)}.
%\]
\end{lemma}

@@

\begin{proofof}{Theorem~\ref{thm:mainktoinfty}}
We first rewrite $c(k_n; G_n)$ as
\begin{align*}
    c(k_n;G_n)-\gamma(k_n) &= \left(c(k_n;G_n)-c^\ast(k_n;G_n)\right)
    	+ \left(c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)\right)\\
    &\hspace{10pt}+ \left(c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right)
    	+ \left(c^\ast(k_n; \Gbox)-\Exp{c^\ast(k_n; \Gbox)}\right)\\
    &\hspace{10pt}+ \Exp{c^\ast(k_n; \Gbox)}-\gamma(k_n)
\end{align*}
Then, we take absolute values and apply the triangle inequality. 
\begin{align*}
    \left|c(k_n;G_n)-\gamma(k_n)\right|
    &\le \left|c(k_n;G_n)-c^\ast(k_n;G_n)\right|
    	+\left|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)\right|\\
    &\hspace{10pt}+ \left|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right|
    	+ \left|c^\ast(k_n; \Gbox)-\Exp{c^\ast(k_n; \Gbox)}\right|\\
    &+ \left|\Exp{c^\ast(k_n; \Gbox)}-\gamma(k_n)\right|
\end{align*}
The first term is $\smallOp{s(k_n)}$ by Lemma~\ref{lem:clustering_ast_H}. For the other terms, the propositions presented above in this section can be applied in order to show that the expectation of each difference is $\smallO{s(k_n)}$: Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling between the Poissonized KPKVB and the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model.

In particular, this implies that all terms are $\smallOp{s(k_n)}$. We thus conclude that
\begin{align*}
    \left|c(k_n;G_n)-\gamma(k_n)\right| = \smallOp{s(k_n)} = \smallOp{\gamma(k_n)},
\end{align*}
which establishes the first statement of the theorem and finishes the proof.  
\end{proofof}
